\section*{Acknowledgements}
%The analyses presented in this thesis 
%I wish to deeply acknowledge for the completion of this thesis work my supervisor, Wolfgang Löffler
\begin{comment}
This thesis work would not have been possible without my supervisor Wolfgang Löffler and Mio Poortvliet, i want to deeply thank you for accepting me in your research group. I enjoyed every single moment i spent here.
i want to account in particular the leadership and the teachings Wolfgang Löffler, it has been a true pleasure to work and learn from you.
From the very first moments and up until the last steps, your presence has never diminished, and it resulted in being the most stable contact among these months. 
Although i always wanted to avoid disturbing your schedule too much, every time we met you have been always on point and straight to the point.
An honorable mention also to my research group, for accepting me into your work environment and sharing some valuable insights on the dutch culture that i was completely unaware of as a first year student abroad.
Finally, i can not thank enough Kirsten for contributing heavily to my personal development and Saqib for the amazing bond we developed since the beginning of your employment here.
\end{comment}

This thesis would not have been possible without the guidance and support of my supervisor,  Wolfgang Löffler, and my co-supervisor, Mio Poortvliet.
Thank you for welcoming me into your research group and guiding me throughout this project.
Dear Wolfgang, your leadership, insightful feedback, and ability to provide clear, focused guidance during our meetings have been invaluable. It has been a true privilege to learn from you.

I also extend my gratitude to my research group for creating a welcoming and collaborative environment. Your willingness to share knowledge and insights into Dutch culture greatly enriched my experience as a first-year international student. 

Special thanks go to Kirsten, whose encouragement and support significantly contributed to my personal growth, and to Ramon, Ali and Saqib, whose friendship made my time here truly memorable.

Finally, I am profoundly grateful to my family and friends for their endless encouragement and belief in me throughout this endeavor.